---
title: "3_Models"
output: html_document
---

```{r}
#clean
rm(list = ls())

library("pacman")
p_load(tidyverse, here, haven, countrycode, sjPlot, lme4, survey, broom,
       marginaleffects, ggeffects, srvyr, patchwork, ggeffects, ragg,
       flextable, officer, sf, rnaturalearth, scales, ggrepel)

```


# Input

```{r}
# Load
lon_turn_df = readRDS(here("Input", "data_clean.rds"))
```

# Processing

```{r}
# weights
ess_design <- svydesign(
 ids = ~psu, 
 strata = ~stratum, 
 weights = ~anweight, 
 data = lon_turn_df, 
 nest = TRUE
)

#as_survey_design
ess_survey <- lon_turn_df %>%
  as_survey_design(
    ids = psu, 
    strata = stratum, 
    weights = anweight, 
    nest = TRUE
  )
```

```{r}
# Global options for plots

# Custom theme
theme_paper <- function() {
  theme_bw(base_size = 12) +
    theme(
      text = element_text(family = "serif", color = "black"), 
      plot.title = element_text(face = "bold", size = 14, margin = margin(b = 10)),
      plot.subtitle = element_text(size = 11, color = "grey40", margin = margin(b = 10)),
      axis.title = element_text(face = "bold", size = 12),
      axis.text = element_text(size = 10, color = "black"),
      axis.text.x = element_text(angle = 45, hjust = 1, face = "bold"),
      strip.background = element_blank(), 
      strip.text = element_text(face = "bold", size = 11),
      panel.border = element_rect(color = "black", linewidth = 0.8), 
      panel.grid.minor = element_blank(), 
      panel.grid.major.x = element_blank(),
      legend.position = "bottom",
      legend.title = element_text(face = "bold"),
      legend.key = element_blank()
    )
}

# Lock it in 
theme_set(theme_paper())

#Global palette
magma_pal <- c("#0D0887FF", "#6A00A8FF", "#B12A90FF", "#E16462FF", "#FCA636FF", "#F0F921FF")
```

## Multilevel model

```{r}
# Data prep

mlm_df <- lon_turn_df %>%
  # STEP 1: STRICT LISTWISE DELETION ON RAW VARIABLES
  drop_na(
    vote_strict, vote,                 
    lon_n, si_n,                       
    lon, si_levels, sil_type,          
    polint_n, partisanship,            
    official_turnout_lag,              
    gender, age, educ, hhincome        
  ) %>%
  
  # STEP 2: Merge extremes of SI. 
  mutate(
    si_n = ifelse(si_n >= 5, 5, si_n)
  ) %>%
  
  # STEP 3: GROUP-MEAN Z-SCORE STANDARDIZATION
  group_by(cntry) %>%
  mutate(
    # Age stays strictly group-mean centered 
    age_centered = age - mean(age),
    
    # Standardize all individual-level numeric variables (Z-scores)
    polint_centered = (polint_n - mean(polint_n)) / sd(polint_n), 
    lon_centered    = (lon_n - mean(lon_n)) / sd(lon_n),
    si_centered     = (si_n - mean(si_n)) / sd(si_n)
  ) %>%
  ungroup() %>%
  
  # STEP 4: FINAL MLM TRANSFORMATIONS
  mutate(
    age_decades_centered = age_centered / 10,
    weights_scaled = anweight / mean(anweight),
    
    # The exhaustive typology relies on the 3-level categorical vars, so it remains unaffected
    sil_exhaustive = interaction(lon, si_levels, sep = " & "),
    sil_exhaustive = relevel(sil_exhaustive, ref = "None/Almost none & 0-1: Low ISO")
  )
```


```{r}
# Sample size per wave, table

# Calculate N by country 
n_by_cntry_clean <- mlm_df %>%
  count(cntry, name = "Final_N") %>%
  # Translate ISO codes to full country names
  mutate(Country = countrycode(cntry, origin = "iso2c", destination = "country.name")) %>%
  # Select and rename 
  select(Country, `Final Sample Size (N)` = Final_N) %>%
  arrange(Country)

# Flextable
ft_n <- flextable(n_by_cntry_clean)
ft_n <- bold(ft_n, part = "header")
# Center everything
ft_n <- align(ft_n, align = "center", part = "all")
ft_n <- align(ft_n, j = 1, align = "left", part = "body") 
ft_n <- autofit(ft_n)

# save
doc_n <- read_docx()
doc_n <- body_add_par(doc_n, "Final Analytical Sample Size by Country", style = "heading 1")
doc_n <- body_add_flextable(doc_n, ft_n)
print(
  doc_n,
  target = here("Output", "Supplement", "Final_Sample_Size_By_Country.docx")
)
```

```{r}
typology <- data.frame(
  ` ` = c("Low Social Isolation", "High Social Isolation"),
  `Low Loneliness` = c(
    "Socially Integrated",
    "Solitary but Content"
  ),
  `High Loneliness` = c(
    "Emotionally Disconnected",
    "Socially Disconnected"
  )
)

ft <- flextable(typology)
ft <- bold(ft, part = "header")
ft <- bold(ft, j = 1)
ft <- align(ft, align = "center", part = "all")
ft <- autofit(ft)

doc <- read_docx()
doc <- body_add_par(doc, "Typology of Social Isolation and Loneliness", style = "heading 1")
doc <- body_add_flextable(doc, ft)

print(
  doc,
  target = here("Output", "Article", "typology_table.docx")
)
```

### Main models

#### Justification for random slopes

```{r}
# test 1
test0_intercept <- suppressWarnings(glmer(
  vote_strict ~ lon_centered + si_centered + gender + age_decades_centered + educ + hhincome + (1 | cntry), 
  data = mlm_df, family = binomial, weights = weights_scaled,
  control = glmerControl(optimizer = "bobyqa")
))

# test 2
test1_lon_slope <- suppressWarnings(glmer(
  vote_strict ~ lon_centered + si_centered + gender + age_decades_centered + educ + hhincome + (1 + lon_centered | cntry), 
  data = mlm_df, family = binomial, weights = weights_scaled,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e5))
))

# test 3
test2_both_slopes <- suppressWarnings(glmer(
  vote_strict ~ lon_centered + si_centered + gender + age_decades_centered + educ + hhincome + (1 + lon_centered + si_centered | cntry), 
  data = mlm_df, family = binomial, weights = weights_scaled,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
))

# anova
anova(test0_intercept, test1_lon_slope, test2_both_slopes)
```

#### MM1-MM3

```{r}
# MM1 to MM3
mm1 <- suppressWarnings(glmer(
  vote_strict ~ lon_centered + official_turnout_lag + gender + age_decades_centered + educ + hhincome + (1 + lon_centered | cntry), 
  data = mlm_df, family = binomial, weights = weights_scaled,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
))

# MM2 
mm2 <- suppressWarnings(glmer(
  vote_strict ~ lon_centered + si_centered + official_turnout_lag + gender + age_decades_centered + educ + hhincome + (1 + lon_centered | cntry), 
  data = mlm_df, family = binomial, weights = weights_scaled,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
))

# MM3 
mm3 <- suppressWarnings(glmer(
  vote_strict ~ lon_centered + si_centered + polint_centered + partisanship + official_turnout_lag + gender + age_decades_centered + educ + hhincome + (1 + lon_centered | cntry), 
  data = mlm_df, family = binomial, weights = weights_scaled,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
))
```

### Robustness / alternative specifications

#### MM3_1 - MM3_4

```{r}
mm3_1 <- suppressWarnings(glmer(
  vote_strict ~ lon_centered * si_centered + polint_centered + partisanship + official_turnout_lag + gender + age_decades_centered + educ + hhincome + (1 + lon_centered | cntry), 
  data = mlm_df, family = binomial, weights = weights_scaled,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
))

# MM3_2 (Fixed random slope)
mm3_2 <- suppressWarnings(glmer(
  vote ~ lon_centered + si_centered + polint_centered + partisanship + official_turnout_lag + gender + age_decades_centered + educ + hhincome + (1 + lon_centered | cntry), 
  data = mlm_df, family = binomial, weights = weights_scaled,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
))

# MM3_3 (Fixed random slope)
mm3_3 <- suppressWarnings(glmer(
  vote_strict ~ lon_centered * official_turnout_lag + si_centered + polint_centered + partisanship + gender + age_decades_centered + educ + hhincome + (1 + lon_centered | cntry), 
  data = mlm_df, family = binomial, weights = weights_scaled,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
))

# MM3_4 (Fixed random slope)
mm3_4 <- suppressWarnings(glmer(
  vote_strict ~ lon_centered + si_centered * official_turnout_lag + polint_centered + partisanship + gender + age_decades_centered + educ + hhincome + (1 + lon_centered | cntry), 
  data = mlm_df, family = binomial, weights = weights_scaled,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
))
```


#### Typology and robustness of typology

```{r}
mm4_typo <- suppressWarnings(glmer(
  vote_strict ~ sil_type + gender + age_decades_centered + educ + hhincome + (1 | cntry), 
  data = mlm_df, family = binomial, weights = weights_scaled,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
))

mm4_robust <- suppressWarnings(glmer(
  vote_strict ~ sil_exhaustive + gender + age_decades_centered + educ + hhincome + (1 | cntry), 
  data = mlm_df, family = binomial, weights = weights_scaled,
  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))
))
```


### Save/load all the models

```{r}
saveRDS(test0_intercept, here("Input", "Models", "test0_intercept.rds"))
saveRDS(test1_lon_slope, here("Input", "Models", "test1_lon_slope.rds"))
saveRDS(test2_both_slopes, here("Input", "Models", "test2_both_slopes.rds"))

saveRDS(mm1, here("Input", "Models", "mm1.rds"))
saveRDS(mm2, here("Input", "Models", "mm2.rds"))
saveRDS(mm3, here("Input", "Models", "mm3.rds"))

saveRDS(mm3_1, here("Input", "Models", "mm3_1.rds"))
saveRDS(mm3_2, here("Input", "Models", "mm3_2.rds"))
saveRDS(mm3_3, here("Input", "Models", "mm3_3.rds"))
saveRDS(mm3_4, here("Input", "Models", "mm3_4.rds"))

saveRDS(mm4_typo, here("Input", "Models", "mm4_typo.rds"))
saveRDS(mm4_robust, here("Input", "Models", "mm4_robust.rds"))
```

```{r}
# or load them all
test0_intercept <- readRDS(here("Input", "Models", "test0_intercept.rds"))
test1_lon_slope <- readRDS(here("Input", "Models", "test1_lon_slope.rds"))
test2_both_slopes <- readRDS(here("Input", "Models", "test2_both_slopes.rds"))

mm1 <- readRDS(here("Input", "Models", "mm1.rds"))
mm2 <- readRDS(here("Input", "Models", "mm2.rds"))
mm3 <- readRDS(here("Input", "Models", "mm3.rds"))

mm3_1 <- readRDS(here("Input", "Models", "mm3_1.rds"))
mm3_2 <- readRDS(here("Input", "Models", "mm3_2.rds"))
mm3_3 <- readRDS(here("Input", "Models", "mm3_3.rds"))
mm3_4 <- readRDS(here("Input", "Models", "mm3_4.rds"))

mm4_typo <- readRDS(here("Input", "Models", "mm4_typo.rds"))
mm4_robust <- readRDS(here("Input", "Models", "mm4_robust.rds"))
```


## Regression tables

```{r}
# Labels

# Table S1 
lbl_s1 <- c("Intercept", "Loneliness (Standardized)", "Social Isolation (Standardized)", "Gender: Female", 
            "Age (Decades)", "Education: Medium", "Education: High", 
            "Income: Coping", "Income: Difficult", "Income: Very Difficult")

# Table 1 (MM1, MM2, MM3 merged)
lbl_t1 <- c("Intercept", "Loneliness (Standardized)", "Official Turnout (Lag)", "Gender: Female", 
            "Age (Decades)", "Education: Medium", "Education: High", 
            "Income: Coping", "Income: Difficult", "Income: Very Difficult", 
            "Social Isolation (Standardized)", "Political Interest (Standardized)", "Partisanship: Yes")

# Table S2 
lbl_s2 <- c("Intercept", "Loneliness (Standardized)", "Social Isolation (Standardized)", "Political Interest (Standardized)", 
            "Partisanship: Yes", "Official Turnout (Lag)", "Gender: Female", "Age (Decades)", 
            "Education: Medium", "Education: High", "Income: Coping", "Income: Difficult", 
            "Income: Very Difficult", "Loneliness × Social Isolation")

# Table S3 
lbl_s3 <- c("Intercept", "Loneliness (Standardized)", "Social Isolation (Standardized)", "Political Interest (Standardized)", 
            "Partisanship: Yes", "Official Turnout (Lag)", "Gender: Female", "Age (Decades)", 
            "Education: Medium", "Education: High", "Income: Coping", "Income: Difficult", "Income: Very Difficult")

# Table S4 
lbl_s4 <- c("Intercept", "Loneliness (Standardized)", "Official Turnout (Lag)", "Social Isolation (Standardized)", 
            "Political Interest (Standardized)", "Partisanship: Yes", "Gender: Female", "Age (Decades)", 
            "Education: Medium", "Education: High", "Income: Coping", "Income: Difficult", 
            "Income: Very Difficult", "Loneliness × Official Turnout")

# Table S5 
lbl_s5 <- c("Intercept", "Loneliness (Standardized)", "Social Isolation (Standardized)", "Official Turnout (Lag)", 
            "Political Interest (Standardized)", "Partisanship: Yes", "Gender: Female", "Age (Decades)", 
            "Education: Medium", "Education: High", "Income: Coping", "Income: Difficult", 
            "Income: Very Difficult", "Social Isolation × Official Turnout")

# Table 2 
lbl_t2 <- c("Intercept", "Typology: Lonely & Connected", "Typology: Isolated & Not Lonely", 
            "Typology: Double Disadvantage", "Gender: Female", "Age (Decades)", 
            "Education: Medium", "Education: High", "Income: Coping", "Income: Difficult", "Income: Very Difficult")

# Table S6 
lbl_s6 <- c("Intercept", "Typology: None & Mid ISO", "Typology: None & High ISO", 
            "Typology: Some & Low ISO", "Typology: Some & Mid ISO", "Typology: Some & High ISO", 
            "Typology: Most & Low ISO", "Typology: Most & Mid ISO", "Typology: Most & High ISO", 
            "Gender: Female", "Age (Decades)", "Education: Medium", "Education: High", 
            "Income: Coping", "Income: Difficult", "Income: Very Difficult")
```


```{r}
# export tabs

# Justify slopes
tab_model(
  test0_intercept, test1_lon_slope, test2_both_slopes,
  show.re.var = TRUE, show.icc = TRUE,
  pred.labels = lbl_s1,
  p.style = "scientific_stars",
  show.p = F,
  dv.labels = c("Test 0: Intercept Only", "Test 1: Loneliness Slope", "Test 2: Full Random Slopes"),
  file = here("Output", "Supplement", "Tables", "Justify_Random_Slopes.doc")
)

# 1: Nested MM1, MM2, MM3
tab_model(
  mm1, mm2, mm3,
  show.re.var = TRUE, show.icc = TRUE,
  pred.labels = lbl_t1,
  p.style = "scientific_stars",
  show.p = F,
  dv.labels = c("MM1: Loneliness Base", "MM2: Add Isolation", "MM3: Full Model"),
  file = here("Output", "Supplement", "Tables", "MM1_MM3.doc")
)

# 2: Robustness (interaction) 
tab_model(
  mm3_1,
  show.re.var = TRUE, show.icc = TRUE,
  pred.labels = lbl_s2,
  p.style = "scientific_stars",
  show.p = F,
  dv.labels = "MM3_1: Interaction",
  file = here("Output", "Supplement", "Tables", "mm3_1.doc")
)

# 3: Robustness (other DV) 
tab_model(
  mm3_2,
  show.re.var = TRUE, show.icc = TRUE,
  pred.labels = lbl_s3,
  p.style = "scientific_stars",
  show.p = F,
  dv.labels = "MM3_2: Self-Reported Vote",
  file = here("Output", "Supplement", "Tables", "mm3_2.doc")
)

# 4: Robustness (cross-level lon x turnout) 
tab_model(
  mm3_3,
  show.re.var = TRUE, show.icc = TRUE,
  pred.labels = lbl_s4,
  p.style = "scientific_stars",
  show.p = F,
  dv.labels = "MM3_3: Cross-Level",
  file = here("Output", "Supplement", "Tables", "mm3_3.doc")
)

# 5: Robustness (cross-level SI x turnout) ---
tab_model(
  mm3_4,
  show.re.var = TRUE, show.icc = TRUE,
  pred.labels = lbl_s5,
  p.style = "scientific_stars",
  show.p = F,
  dv.labels = "MM3_4: Cross-Level",
  file = here("Output", "Supplement", "Tables", "Table_S5_CrossLevel_SI.doc")
)

# 6: Typology 
tab_model(
  mm4_typo,
  show.re.var = TRUE, show.icc = TRUE,
  pred.labels = lbl_t2,
  p.style = "scientific_stars",
  show.p = F,
  dv.labels = "MM4: Typology Base",
  file = here("Output", "Supplement", "Tables", "mm4_typo.doc")
)

# 7: Typology exhaustive
tab_model(
  mm4_robust,
  show.re.var = TRUE, show.icc = TRUE,
  pred.labels = lbl_s6,
  p.style = "scientific_stars",
  show.p = F,
  dv.labels = "MM4: Typology Exhaustive",
  file = here("Output", "Supplement", "Tables", "mm4_robust.doc")
)
```


## Plots

### Caterpillar 

```{r}
# Base: random effects plots
re_plots <- plot_model(
  mm3, type = "re", 
  sort.est = "sort.all", 
  grid = FALSE, 
  colors = magma_pal[1],
  dot.size = 2.5, 
  line.size = 0.8,
  transform = "exp"
)

# From ISO to full names
clean_country_labels <- function(x) {
  countrycode(x, origin = "iso2c", destination = "country.name")
}

# Extract and polish panel A: RI
p_intercepts <- re_plots[[1]] + 
  scale_x_discrete(labels = clean_country_labels) +
  theme_paper() +
  labs(
    title = "Baseline turnout by country",
    y = "Deviation from Average Penalty (Odds Ratio)", 
    x = ""
  ) +
  theme(
    panel.grid.major.y = element_line(color = "grey90", linetype = "dashed"),
    axis.text.y = element_text(size = 10, face = "bold") 
  )

# Extract and polish panel B: loneliness slopes
p_lon_slopes <- re_plots[[2]] + 
  scale_x_discrete(labels = clean_country_labels) +
  theme_paper() +
  labs(
    title = "Loneliness penalty by country",
    y = "Deviation from Average Penalty (Log-Odds)", 
    x = ""
  ) +
  theme(
    panel.grid.major.y = element_line(color = "grey90", linetype = "dashed"),
    axis.text.y = element_text(size = 10, face = "bold",
                               ) 
  )

# Combine 
figure1_combined <- p_intercepts + p_lon_slopes + 
  plot_layout(ncol = 2)

# Save  
ggsave(
  here("Output", "Supplement", "Caterpillar.png"), 
  figure1_combined, 
  width = 12, 
  height = 16, 
  dpi = 600,
  bg = "white"
)

```

### Choropleth

```{r}
# Map of lon penalty

# Extract and format the random slope deviations
re_vals <- ranef(mm3)$cntry
re_df <- re_vals %>%
  rownames_to_column("cntry") %>%
  # Convert log-odds to relative percentage change
  mutate(lon_dev_rel = exp(lon_centered) - 1) %>%
  # country to 3-letter ISO
  mutate(iso3c = countrycode(cntry, origin = "iso2c", destination = "iso3c")) %>%
  select(iso3c, lon_dev_rel)

# use admin names, ISO do not work
world_map <- ne_countries(scale = "medium", returnclass = "sf") %>%
  mutate(iso3c = countrycode(admin, origin = "country.name", destination = "iso3c"))

# Merge 
map_data <- world_map %>%
  left_join(re_df, by = "iso3c")

# Plot the Choropleth Map
p_map <- ggplot(data = map_data) +
  geom_sf(aes(fill = lon_dev_rel), color = "white", size = 0.3) +
  
  # Tighter crop strictly on Europe
  coord_sf(xlim = c(-25, 42), ylim = c(29, 73), expand = FALSE) +

  scale_fill_gradientn(
    colors = rev(magma_pal),
    name = "Deviation from\nAverage Penalty",
    labels = scales::percent_format(accuracy = 1),
    na.value = "grey90" 
  ) +
  
  # no labs
  labs(title = NULL, subtitle = NULL, x = NULL, y = NULL) +
  
  theme_paper() +
  theme(
    # remove all graphical elements
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_blank(),
    axis.text.x = element_blank(), 
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank(),
    
    # Remove all borders and backgrounds 
    panel.border = element_blank(),
    panel.background = element_blank(),
    plot.background = element_blank(),
    
    legend.position = "right",
    legend.key.height = unit(1, "cm")
  )

# Save 
ggsave(
  here("Output", "Article", "Figure2_Map.png"), 
  p_map, 
  width = 10, 
  height = 8, 
  dpi = 600,
  bg = "white"
)

ggsave(
  here("Output", "Article", "Figure2_Map.pdf"), 
  p_map, 
  width = 10, 
  height = 8, 
  device = "pdf",
  dpi = 600,
  bg = "white"
)
```

### Scatter lon / lon penalty

```{r}
# Calculate the average loneliness score 
country_means <- mlm_df %>%
  group_by(cntry) %>%
  summarize(mean_lon = mean(lon_n, na.rm = TRUE))

# extract RS and convert to percentage deviation
re_vals <- ranef(mm3)$cntry %>%
  rownames_to_column("cntry") %>%
  # as we did in the map!
  mutate(lon_dev_rel = exp(lon_centered) - 1) %>%
  select(cntry, lon_dev_rel)

# Merge 
scatter_df <- left_join(country_means, re_vals, by = "cntry")

# Scatterplot
p_scatter <- ggplot(scatter_df, aes(x = mean_lon, y = lon_dev_rel)) +
  

  geom_hline(yintercept = 0, linetype = "dashed", color = "grey70", linewidth = 0.8) +
  geom_point(color = magma_pal[2], size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = FALSE, color = magma_pal[4], linetype = "solid", linewidth = 1) +
  
  # Add the 2-digit country codes, repelled 
  geom_text_repel(aes(label = cntry), size = 4, fontface = "bold", color = "black",
                  box.padding = 0.4, point.padding = 0.3) +
  
  # Format the Y axis 
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  
  # no title and labs
  labs(
    title = NULL,
    subtitle = NULL,
    x = "Mean Loneliness Score (1-3 Scale)",
    y = "Deviation from\nAverage Penalty"
  ) +
  
  theme_paper() +
  theme(
    panel.grid.major = element_line(color = "grey95")
  )

# Save 
ggsave(
  here("Output", "Article", "Figure_Scatterplot_Loneliness.png"), 
  p_scatter, 
  width = 8,      
  height = 3.9,   
  dpi = 600,
  bg = "white"
)

ggsave(
  here("Output", "Article", "Figure_Scatterplot_Loneliness.pdf"), 
  p_scatter, 
  width = 8,      
  height = 3.9,   
  device = "pdf",
  dpi = 600,
  bg = "white"
)
```


```{r}
# Stats shown in the article

# the actural cor
cor_test <- cor.test(scatter_df$mean_lon, scatter_df$lon_dev_rel)
cor_test

#the penalty is not dictated by sample size
sample_sizes <- mlm_df %>%
  count(cntry, name = "sample_size")

re_vals_check <- ranef(mm3)$cntry %>%
  rownames_to_column("cntry") %>%
  mutate(lon_penalty_or = exp(lon_centered)) %>%
  select(cntry, lon_penalty_or)

check_df <- left_join(sample_sizes, re_vals_check, by = "cntry")

cor.test(check_df$sample_size, check_df$lon_penalty_or)
```


### Predicted turnout 4 panels

```{r}
# Helper function
create_minmax_plot <- function(model, term, labels, plot_title, dot_color) {
  # predictions
  df <- as.data.frame(ggpredict(model, terms = paste0(term, " [minmax]")))
  
  ggplot(df, aes(x = factor(x, levels = unique(x), labels = labels), y = predicted)) +
    # Reference line 
    geom_hline(yintercept = mean(df$predicted), color = "grey60", alpha = 0.5, linewidth = 1.2, linetype = "dashed") +
    # Point range for CIs
    geom_pointrange(aes(ymin = conf.low, ymax = conf.high),
                    linewidth = 0.8, fatten = 2.5, color = dot_color) +
    # Y-axis 
    scale_y_continuous(limits = c(0.30, 0.9), breaks = seq(0.3, 0.9, .1), labels = scales::percent) +
    labs(x = NULL, y = "Pr(Turnout)", title = plot_title) +
    theme_paper() + 
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.major.y = element_line(color = "grey95"),
      plot.title = element_text(hjust = 0.5, face = "bold", size = 16), 
      axis.title.y = element_text(size = 14, face = "bold"),
      axis.text = element_text(color = "black", size = 12), 
      axis.text.x = element_text(angle = 0, hjust = 0.5, size = 13, face = "bold") 
    )
}

# Generate 
# Panel A: Loneliness
p_A <- create_minmax_plot(mm3, "lon_centered", c("Min.\nLoneliness", "Max.\nLoneliness"), "Loneliness", magma_pal[4])

# Panel B: Social Isolation
p_B <- create_minmax_plot(mm3, "si_centered", c("Min.\nIsolation", "Max.\nIsolation"), "Social Isolation", magma_pal[2])

# Panel C: Political Interest
p_C <- create_minmax_plot(mm3, "polint_centered", c("Min.\nInterest", "Max.\nInterest"), "Political Interest", magma_pal[5])

# Panel D: Partisanship
p_D <- create_minmax_plot(mm3, "partisanship", c("Party Closeness:\nNo", "Party Closeness:\nYes"), "Party Closeness", magma_pal[1])

# Together
figure2 <- (p_A + p_B) / (p_C + p_D) + 
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(face = "bold", size = 18))

# Save 
ggsave(here("Output", "Article", "pred_prob.png"), plot = figure2, width = 12, height = 16, dpi = 600)

# Stats presented in text:
p_A$data
p_B$data
p_C$data
p_D$data
```

### Typo plot

```{r}
# predictions 
df_typo <- as.data.frame(ggpredict(mm4_typo, terms = "sil_type"))

# Plot
p_typo <- ggplot(df_typo, aes(x = reorder(x, -predicted), y = predicted, color = x)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), linewidth = 1.2, fatten = 3) +
  
  # Y axis 
  scale_y_continuous(labels = scales::percent, limits = c(0.4, 0.7), breaks = seq(0.4, 0.7, 0.1)) +
  
  # colors
  scale_color_manual(values = c(magma_pal[1], magma_pal[2], magma_pal[4], magma_pal[5])) +
  
  # injects \n 
  scale_x_discrete(labels = function(lbl) gsub(", ", ",\n", lbl)) +
  
  labs(
    x = NULL, 
    y = "Pr(Turnout)",
  ) +
  theme_paper() +
  theme(
    legend.position = "none", 
    
    # Graphical settings 
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(color = "grey95"),
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16), 
    axis.title.y = element_text(size = 14, face = "bold"),
    axis.text = element_text(color = "black", size = 12),
    axis.text.x = element_text(angle = 0, hjust = 0.5, size = 13, face = "bold") 
  )

# Save
ggsave(here("Output", "Article", "Figure3_Typology.png"), p_typo, width = 9, height = 6, dpi = 600)

#stats for the article
p_typo$data
```


### Exhaustive typo plot

This plot shows that the result of the main typo model presented in the article 
are robust to any ways in which u cut the typology var.

```{r}
# some extra packages
library(ggeffects)
library(dplyr)
library(ggplot2)
library(scales)
library(tidyr)
library(patchwork) 


# Take pred turnout
pred_turnout <- ggpredict(mm4_robust, terms = "sil_exhaustive") %>%
  as_tibble() %>%
  rename(sil_exhaustive = x, predicted_turnout = predicted, conf_low = conf.low, conf_high = conf.high)

# Calculate actual population share
group_sizes <- mlm_df %>%
  drop_na(vote_strict, sil_exhaustive, gender, age_decades_centered, educ, hhincome) %>%
  count(sil_exhaustive) %>%
  mutate(pop_share = n / sum(n))

# Merge
plot_df <- left_join(pred_turnout, group_sizes, by = "sil_exhaustive") %>%
  mutate(
    si_level = case_when(
      grepl("0-1: Low ISO", sil_exhaustive) ~ "Low",
      grepl("2: Mid ISO", sil_exhaustive) ~ "Mid",
      grepl("3\\+: High ISO", sil_exhaustive) ~ "High"
    ),
    lon_level = case_when(
      grepl("None/Almost none", sil_exhaustive) ~ "Low",
      grepl("Some of the time", sil_exhaustive) ~ "Mid",
      grepl("Most/All the time", sil_exhaustive) ~ "High"
    )
  )

# fix x axis order
plot_df$category_id <- reorder(plot_df$sil_exhaustive, desc(plot_df$predicted_turnout))

# Plot 1: bubble chart
p_main <- ggplot(plot_df, aes(x = category_id, y = predicted_turnout)) +
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high), width = 0.1, color = "grey60", alpha = 0.6) +
  
  # geom point
  geom_point(aes(size = pop_share), fill = "#FFB74D", shape = 21, color = "white", stroke = 1.2) +
  
  # color of text
  geom_text(aes(label = percent(pop_share, accuracy = 1)), color = "black", fontface = "bold", size = 3.5) +
  
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_size_continuous(range = c(8, 26), guide = "none") +
  labs(x = NULL, y = "Predicted Turnout Probability", title = NULL, subtitle = NULL) +
  theme_paper() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(color = "grey90", linetype = "dashed"),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    plot.margin = margin(t = 20, r = 20, b = -5, l = 20),
    legend.position = "none"
  )

# Plot 2: heatmap
axis_df <- plot_df %>%
  select(category_id, si_level, lon_level) %>%
  pivot_longer(cols = c(si_level, lon_level), names_to = "variable", values_to = "intensity") %>%
  mutate(
    variable = ifelse(variable == "si_level", "Social\nIsolation", "Loneliness"),
    variable = factor(variable, levels = c("Loneliness", "Social\nIsolation")),
    intensity = factor(intensity, levels = c("Low", "Mid", "High"))
  )

p_axis <- ggplot(axis_df, aes(x = category_id, y = variable, fill = intensity)) +
  geom_tile(color = "white", linewidth = 1.5, width = 0.9, height = 0.9) +
  geom_text(aes(label = intensity, color = intensity), fontface = "bold", size = 3.5) +
  
  # Traffic light colors 
  scale_fill_manual(values = c("Low" = "#E0E0E0", "Mid" = "#FFB74D", "High" = "#E53935")) +
  scale_color_manual(values = c("Low" = "black", "Mid" = "black", "High" = "white")) +
  
  theme_void() +
  theme(
    axis.text.y = element_text(face = "bold", color = "black", size = 9, hjust = 1, margin = margin(r = 5)),
    legend.position = "none",
    plot.caption = element_text(hjust = 0, face = "italic", color = "grey40", size = 9, margin = margin(t = 15)),
    plot.margin = margin(t = 0, r = 20, b = 20, l = 20)
  ) +
  labs(caption = "Note: Bubble size indicates the percentage of the sample in each typology group.\nPredicted probabilities are population-averaged marginal effects, calculated holding controls at their means and generalizing across all countries.")

# put togethert
final_plot <- p_main / p_axis + plot_layout(heights = c(6, 1))

# Save
ggsave(
  here("Output", "Supplement", "Figure_Targeting_Dilemma_HeatmapAxis.png"), 
  final_plot, 
  width = 12, 
  height = 7.5, 
  dpi = 600,
  bg = "white"
)

```

This is instead a plot we used for a presentation of this work, where we show 
the interplay between how many people you target and the severity of SIL penalty 
on turnout

```{r}
library(ggeffects)
library(dplyr)
library(ggplot2)
library(scales)
library(patchwork)
library(ggrepel)

# Predictions from the exhaustive model
pred_turnout <- ggpredict(mm4_robust, terms = "sil_exhaustive") %>% 
  as_tibble() %>% 
  rename(sil_exhaustive = x, predicted_turnout = predicted, conf_low = conf.low, conf_high = conf.high)

# population sizes
group_sizes <- mlm_df %>% 
  drop_na(vote_strict, sil_exhaustive, gender, age_decades_centered, educ, hhincome) %>% 
  count(sil_exhaustive) %>%
  mutate(pop_share = n / sum(n))

plot_df <- left_join(pred_turnout, group_sizes, by = "sil_exhaustive")
total_sample <- sum(plot_df$n)

# build the three scenarios 
build_scenario <- function(df, name, id) {
  df %>%
    summarise(
      Scenario = name,
      Scenario_ID = id,
      pop_share = sum(n) / total_sample,
      predicted_turnout = sum(predicted_turnout * n) / sum(n),
      conf_low = sum(conf_low * n) / sum(n),
      conf_high = sum(conf_high * n) / sum(n)
    )
}

s1_df <- plot_df %>% filter(grepl("High ISO", sil_exhaustive)) 
s2_df <- plot_df %>% filter(grepl("High ISO", sil_exhaustive) & !grepl("None/Almost none", sil_exhaustive)) 
s3_df <- plot_df %>% filter(grepl("High ISO", sil_exhaustive) & grepl("Most/All the time", sil_exhaustive)) 

scenario_df <- bind_rows(
  build_scenario(s1_df, "Broad Target\n(Top 75% Severity)", 1),
  build_scenario(s2_df, "Refined Target\n(Top 50% Severity)", 2),
  build_scenario(s3_df, "Strict Target\n(Top 25% Severity)", 3)
) %>%
  mutate(Scenario = reorder(Scenario, Scenario_ID))

# Plot A: predictions
p_top <- ggplot(scenario_df, aes(x = Scenario_ID, y = predicted_turnout)) +
  geom_linerange(aes(ymin = conf_low, ymax = conf_high), color = "grey30", linewidth = 1) +
  geom_point(aes(size = pop_share), fill = magma_pal[3], shape = 21, color = "white", stroke = 1.5) +
  geom_text_repel(
    aes(label = percent(predicted_turnout, accuracy = 0.1)), 
    color = "black",            
    fontface = "bold", 
    size = 4.5,                 
    nudge_x = 0.3,              
    box.padding = 0.5,          
    point.padding = 1.5,        
    segment.color = "grey50",   
    min.segment.length = 0      
  ) +
  
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_x_continuous(breaks = c(1, 2, 3), labels = scenario_df$Scenario, limits = c(0.5, 3.5)) +
  scale_size_continuous(range = c(12, 30), guide = "none") +
  
  labs(x = NULL, y = "Predicted Turnout Probability") +
  theme_paper() +
  theme(
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(color = "grey90", linetype = "dashed"),
    axis.text.x = element_text(angle = 0, hjust = 0.5, face = "bold", size = 11, color = "black"),
    axis.ticks.x = element_blank(),
    plot.margin = margin(b = 10)
  )

# B: matrices
matrix_shapes <- data.frame(
  Scenario_ID = c(1, 2, 3),
  bg_xmin = c(0.6, 1.6, 2.6), bg_xmax = c(1.4, 2.4, 3.4),
  bg_ymin = c(0, 0, 0),       bg_ymax = c(1, 1, 1),
  cut_x = c(0.8, 2.0, 3.2), 
  cut_y = c(0.75, 0.50, 0.25)
)

p_bottom <- ggplot(matrix_shapes) +
  geom_rect(aes(xmin = bg_xmin, xmax = bg_xmax, ymin = bg_ymin, ymax = bg_ymax), 
            fill = "white", color = "black", linewidth = 0.8) +
  
  geom_rect(aes(xmin = cut_x, xmax = bg_xmax, ymin = bg_ymin, ymax = cut_y), 
            fill = magma_pal[3], alpha = 0.5, color = "black", linewidth = 0.5) +
  
  geom_segment(aes(x = bg_xmin, xend = bg_xmax, y = cut_y, yend = cut_y), color = "grey60", linetype = "dashed") +
  geom_segment(aes(x = cut_x, xend = cut_x, y = bg_ymin, yend = bg_ymax), color = "grey60", linetype = "dashed") +
  
  annotate("text", x = 0.55, y = 0.875, label = "Low L", hjust = 1, size = 3, color = "grey40") +
  annotate("text", x = 0.55, y = 0.375, label = "High L", hjust = 1, size = 3, color = "grey40") +
  annotate("text", x = 0.70, y = 1.05, label = "Low SI", vjust = 0, size = 3, color = "grey40") +
  annotate("text", x = 1.10, y = 1.05, label = "High SI", vjust = 0, size = 3, color = "grey40") +
  
  scale_x_continuous(limits = c(0.5, 3.5)) +
  scale_y_continuous(limits = c(-0.2, 1.2)) +
  
  theme_void() +
  theme(plot.margin = margin(t = 0, b = 10))

# Together with captions
final_slide_plot <- p_top / p_bottom + 
  plot_layout(heights = c(4, 1.5)) +
  plot_annotation(
    caption = "Top panel: predicted turnout for the most exposed groups; bubble sizes are proportional to Ns. \n Bottom panel: size of the targeted groups",
    theme = theme(plot.caption = element_text(hjust = 0, face = "italic", color = "grey40", size = 10, margin = margin(t = 15)))
  )

ggsave(
  here("Output", "Supplement", "Figure_Targeting_Funnel_Dynamic.png"), 
  final_slide_plot, 
  width = 10,     
  height = 6.5,   
  bg = "white"
)
```

